### 2017-10-15 Draft2.tex
Not the apex

	Now I wish to find the number of writes [resize] performs. From [make lemma], I know that [resize] is called at the sizes $$S_R = 0,\ \initcapacitynew,\ \growthfactornew\initcapacitynew,\ \growthfactornew^2\initcapacitynew,\ \ldots\ \growthfactornew^{\lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil - 1}\initcapacitynew$$

	Unlike dynamic arrays, however, the number of writes performed does not equal $i$ if the current size is $i$. It is a function of $i$, however, so I will denote it $\nwritesresizefn(i)$. A formula for $\nwritesnewfn(\varnitems)$ can be expressed in terms of $\nwritesresizefn(i)$:

	$$
	\nwritesnewfn(\varnitems) = n + \sum_{i \in S_R} \nwritesresizefn(i)
	$$

	so the goal is now to find a formula for $\nwritesresizefn(i)$. First note that all of the writing in [resize] comes from the call to [add] on a dynamic array. Let the initial capacity of the dynamic array be $\initcapacity$ and its growth factor be $\growthfactor$. We showed before that

>>>>

	Now I take a look at [resize]. Unlike dynamic arrays, the number of writes performed does not equal $i$ if the current size is $i$. No items are being copied; the only source of writes is adding a buffer to the tail. The goal is to find the number of writes that causes.

	Let $\nwritesresizefn(n)$ denote the total number of writes made by [resize]. From [make lemma], I know that [resize] is called at the sizes

	$$
	S_R = 0,\ \initcapacitynew,\ \growthfactornew\initcapacitynew,\ \growthfactornew^2\initcapacitynew,\ \ldots\ \growthfactornew^{\lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil - 1}\initcapacitynew
	$$

	Let $k$ be the number of times the tail is added to. Since the tail is a dynamic array, the number of writes it makes is $\nwritesfn(k)$. Since we call [resize] $|S_R|$ times and it adds to the tail each time except for the first, $k = |S_R| - 1 = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$. Then the formula for $\nwritesresizefn(n)$ is

	$$
	\nwritesresizefn(n) = k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
	$$

	where $\initcapacity$ $\growthfactor$ are the capacity of the \textit{tail} (not the funnel array). I finally conclude that

	$$
	\nwritesnewfn(n) = n + k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
	$$

	Now I wish to find the number of writes [resize] performs.
